---
title: "Identifier-Only Inputs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Identifier-Only Inputs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Some annotation exports contain database identifiers but no reliable compound
name. `MetaboResolveR` accepts identifier-only rows and records which key
matched the reference database.

```{r setup}
library(MetaboResolveR)
```

HMDB/HMID, PubChem CID, ChEBI, and KEGG identifiers can be supplied without a
name. Placeholder values such as `-`, `N/A`, and empty strings are treated as
missing.

```{r id-only}
input <- data.frame(
  HMID = c("HMDB0000122", "-"),
  `PubChem CID` = c(NA, "2519"),
  `ChEBI ID` = c(NA, NA),
  KEGG = c("C00031", NA),
  check.names = FALSE
)

annotated <- annotate_plasma_metabolites(input)
annotated[, c(
  "metabolite_name",
  "hmdb_id",
  "pubchem_cid",
  "kegg_id",
  "matched_reference_key",
  "reference_metabolite_name",
  "final_annotation_class"
)]
```

If multiple identifiers are present, matching prioritizes structured database
IDs before falling back to normalized names. This makes identifier-only inputs
auditable and avoids forcing users to invent names for uncertain annotations.
