---
title: "MetaboResolveR Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MetaboResolveR Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`MetaboResolveR` resolves post-identification untargeted human plasma
metabolomics tables into evidence-scored annotation outputs. It is designed for
reviewing LC-MS metabolite annotation exports, not for raw peak detection.

```{r setup}
library(MetaboResolveR)
```

The main entry point is `annotate_plasma_metabolites()`.

```{r overview-example}
input <- data.frame(
  Name = c("Glucose", "Caffeine", "Unknown feature"),
  HMDB_ID = c("HMDB0000122", "HMDB0001847", "-"),
  PubChemID = c("5793", "2519", "-"),
  Score = c(0.95, 0.88, 0.50),
  check.names = FALSE
)

annotated <- annotate_plasma_metabolites(input)
annotated[, c("metabolite_name", "matched_reference_key", "final_annotation_class")]
```

Use `export_annotation_report()` when you want a CSV annotation table plus a
compact final-class summary.
