---
title: "Real-Case Workflow With a Public Synthetic Fixture"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Real-Case Workflow With a Public Synthetic Fixture}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The private SD rhythm plasma metabolomics workbook is validated locally only.
This vignette mirrors its column structure with a small public synthetic
fixture, so the workflow can be shared without exposing study data.

```{r setup}
library(plasmaAnnotateR)
```

Read the synthetic fixture. Its columns follow the real vendor-style schema,
including `Name`, `HMDB_ID`, `KEGG_ID`, `Lipidmaps_ID`, `PubChemID`, `m/z`,
`RT (min)`, `IonMode`, and `Score`.

```{r read-fixture}
fixture <- system.file("extdata", "example_real_case_schema.csv", package = "plasmaAnnotateR")
input <- read.csv(fixture, stringsAsFactors = FALSE, check.names = FALSE)
names(input)
```

No explicit `column_map` is required for these aliases.

```{r annotate-fixture}
annotated <- annotate_plasma_metabolites(input)
annotated[, c(
  "Compound_ID",
  "metabolite_name",
  "hmdb_id",
  "pubchem_cid",
  "matched_reference_key",
  "plasma_evidence_sources",
  "final_annotation_class"
)]
```

For the private workbook, the local-only scripts under
`data-raw/real_case/` split the `.xlsx` file into ten CSV chunks, annotate each
chunk, and write summary tables:

```{r local-real-case, eval = FALSE}
source("data-raw/real_case/split_real_case.R")
source("data-raw/real_case/run_real_case_validation.R")
```

Those outputs stay outside the public repository.
