---
title: "Human Plasma Reference Database"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Human Plasma Reference Database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The bundled reference database combines metabolite evidence from curated
plasma, serum, and reference-material sources. It is meant to support
annotation review, not to claim that every matched compound is biologically
endogenous in every cohort.

```{r setup}
library(MetaboResolveR)
```

The source catalog records provenance and update notes.

```{r source-catalog}
catalog <- load_reference_source_catalog()
catalog[, c("source_id", "short_name", "source_kind", "evidence_role")]
```

The full evidence table keeps source-specific flags and identifiers.

```{r evidence-table}
reference <- load_plasma_metabolite_evidence_reference()
dim(reference)
names(reference)
```

The current evidence hierarchy is:

- Gold or core plasma evidence: curated plasma benchmark records, NIST SRM1950,
  and metabolites supported by strong cross-cohort plasma evidence.
- Strong supporting evidence: HMDB biofluid annotations and serum evidence.
- Contextual evidence: single-source or lower-reproducibility plasma evidence.

Identifier matching is intentionally transparent. Annotation rows can match by
HMDB/HMID, PubChem CID, ChEBI, KEGG, or normalized name, and the output column
`matched_reference_key` records which key was used.

```{r identifier-audit}
input <- data.frame(
  metabolite_name = c(NA, NA),
  hmdb_id = c("HMDB0000122", NA),
  pubchem_cid = c(NA, "2519"),
  stringsAsFactors = FALSE
)

score_plasma_evidence(input)[, c(
  "hmdb_id",
  "pubchem_cid",
  "matched_reference_key",
  "reference_metabolite_name",
  "plasma_evidence_sources"
)]
```
